\documentclass[a4paper,cleardoubleempty,BCOR1cm]{scrbook}
\input{header}

\title{Thesis Template}
\author{Denis Heid \thanks{e-mail: denis.heid@student.uni-tuebingen.de}}
\date{\today}
\begin{document}

\input{teaser}

\chapter*{Abstract}
    This thesis introduces \emph{points2mesh}, a novel approach to transform point cloud data into fully-fledged, watertight meshes. 
    Adapted from \emph{pixel2mesh} \cite{wang2018pixel2mesh}, transforming images to meshes, this neural network learns features from unstructured points
    in three-dimensional space and deforms a basic 3D ellipsoidal shape into the final watertight mesh based on these learned features.

    \emph{points2mesh} offers several distinct advantages. As the first deep learning-based method to transform point
    cloud data to watertight meshes while producing competitive results with low inference time, it is a pioneer in its subject-matter.
    Additionally, a \emph{supervised} as well as an \emph{unsupervised} variant is presented.


\chapter*{Zusammenfassung}
    Diese Arbeit stellt \emph{points2mesh} vor, einen neuartigen Ansatz zur Transformation von Punktwolkendaten in manngifaltige Polygonnetze. 
    Dieses neuronale Netzwerk, adaptiert von \emph{pixel2mesh} \cite{wang2018pixel2mesh}, welches Bilder in Polygonnetze umwandelt, lernt Merkmale von unstrukturierten Punkten 
    im dreidimensionalen Raum und verformt ein einfaches 3D Polygonnetz in das endgültige mannigfaltige Polygonnetz, basierend auf diesen erlernten Merkmalen.

    \emph{points2mesh} bietet mehrere Vorteile. Als erste lernbasierte Methode zur Transformation von Punktwolkendaten in mannigfaltige Polygonnetze
    bei gleichzeitiger Erzielung wettbewerbsfähiger Ergebnisse mit geringer Inferenzzeit ist sie ein Pionier in ihrem Fachgebiet.
    Zusätzlich wird sowohl eine beaufsichtigte als auch eine unbeaufsichtigte Lernvariante vorgestellt.


\chapter*{Acknowledgments}
    First and foremost, I would like to thank Fabian Groh for guiding me through this thesis, lending valuable feedback and providing 
    a stream of possible improvements or new avenues to consider. Also, I would like to thank Professor Lensch for allowing me to write
     the thesis at his chair of computer graphics.
    I also have enormous gratitude for my family and Friederike Hanssen, supporting and encouraging me throughout this period.



\tableofcontents

%% braucht kein Mensch ...
%% aber ich mag die :(
%\listoffigures
%\listoftables

\input{content/introduction}

\input{content/background}

\input{content/relatedwork}

\input{content/material}

\input{content/methods}

\input{content/results}

\input{content/evaluation}

\input{content/discussion}

\appendix
\input{content/appendix}


\bibliography{bibliography}

\end{document}

